\plaintitle

### 2015-11-07 Paper/paper.tex
Added partial Evaluation section

>>>>

%TODO: Should be 1/2
\subsection{Evaluation}

The system shall be evaluated by its stability, efficiency, ease of use, and
integration.

Its stability will be evaluated by running a fuzzer software on the different
commands that the backend server accepts. If the fuzzer finds strings that 
causes the backend to crash, show an error, or produce the wrong output then the
system fails the stability test. If this happens, the errors shall be fixed and
the system will again undergo the stability evaluation.

The system's efficiency will be evaluated by running benchmarks on the system.
Information such as requests per second, time per request, and transfer rate
of each function will be collected. The system will also be tested if can 
handle medium and heavy workloads by using load testing tools and services.
These tests will use combinations of the different functions at ratios expected
during actual use of the system.

The system's ease of use will be evaluated through a survey along with additional
criteria about other aspects of the system.
The survey will be done with at least 500 respondents that will test the system
and rate it under the following criteria:
\begin{enumerate}
 \item the ability of the user-interface to be understandable without a manual;
 \item the way how buttons in the user-interface are positioned;
 \item the animations embedded into the user-interface
 \item the responsiveness of the system; and
 \item the additional features of the system.
\end{enumerate}
